Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-03 paper/src/paper.tex
figure fix.

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/full-ANL-Intr.pdf}
  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$ on the
    UniLu-Gaia trace. The average is obtained by resampling the original trace
    60 times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling.}
  \label{fig:all}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaicbandit-ANL-Intr.pdf}

  \caption{Share of the policies chosen by Epsilon-Greedy as a function of
  time. The average choice is obtained by resampling the original trace 60 
times and aggregating by date.}

@@

While this policy obtains an excellent performance, the convergence to a fixed
policy is slow.  This is not harmful \textit{per se} and just means that the
variability in the waiting times is indeed high. Additionally, we observe that
the increasingly dominant policy, LCFS, is the second best overall policy. This
is perhaps due to the estimation bias stemming from the boundary conditions of
the weekly simulations.

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaic-ANL-Intr.pdf}

  \caption{Share of the policies chosen by the Noisy policy. The average choice
  is obtained by resampling the original trace 60 times and aggregating by
  date.}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/full-UniLu-Ga.pdf}
  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$ on the
    UniLu-Gaia trace. The average is obtained by resampling the original trace
    60 times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling.}
  \label{fig:all}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaicbandit-UniLu-Ga.pdf}

  \caption{Share of the policies chosen by Epsilon-Greedy($\Delta=$1 day,
  $\epsilon = 0.5, \lambda = 1 $) as a function of time for the UniLu-Gaia
trace. The average choice is obtained by resampling the original trace 60 times
and aggregating by date.}

@@

While this policy obtains an excellent performance, the convergence to a fixed
policy is slow.  This is not harmful \textit{per se} and just means that it is
difficult to distinguish between the best policies. Additionally, we observe that
the two increasingly dominant policy, LAF and LQF, are the best overall policies.
This means that the estimation converges to the correct point.

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaic-UniLu-Ga.pdf}

  \caption{Share of the policies chosen by the Noisy policy as a function of time
    for the UniLu-Gaia trace. The average choice
  is obtained by resampling the original trace 60 times and aggregating by
  date.}
